Continuous developmental changes in word recognition support language learning across early childhood

### 2025-03-21 paper/paper.Rmd
fix a minor aesthetic issue with the timecourse

#overall plot
d_timecourse_by_age_overall |> 
  filter(age_bin!="<12") |> 
  filter(t_norm>-1000) |> 
  ggplot(aes(x=t_norm, y=accuracy, group=age_bin, color=age_bin)) +
  geom_rect(xmin=2000,xmax=4000,ymin=0,ymax=1.2,fill="#DFDFDF",color="#DFDFDF",alpha=0.05)+
  geom_rect(xmin=200,xmax=2000,ymin=0,ymax=1.2,fill="#F2F2F2",color="#F2F2F2",alpha=0.05)+
  geom_smooth(stat="identity", aes(y=accuracy, ymin=accuracy-sem, ymax=accuracy+sem,fill=age_bin))+
  #geom_smooth(stat="smooth")+
  geom_hline(yintercept=0.5, linetype="dashed")+
  geom_vline(xintercept=0, linetype="solid")+
  #add text
  annotate("text", x=50, y=0.85, label="Label Onset", hjust=0, vjust=0,size=3)+
  annotate("text", x=400, y=0.99, label="SHORT WINDOW",hjust=0, vjust=0,size=2.5)+
  annotate("text", x=1500, y=0.93, label="LONG WINDOW",hjust=0, vjust=0,size=2.5)+
  geom_segment(aes(x = 1000, y = 0.98, xend = 200, yend = 0.98),
               arrow = arrow(type = "closed", angle = 20, length = unit(0.05, "inches")), color="black")+
  geom_segment(aes(x = 1000, y = 0.98, xend = 2000, yend = 0.98),
               arrow = arrow(type = "closed", angle = 20, length = unit(0.05, "inches")), color="black")+
  geom_segment(aes(x = 2000, y = 0.92, xend = 200, yend = 0.92),
               arrow = arrow(type = "closed", angle = 20, length = unit(0.05, "inches")), color="black")+
  geom_segment(aes(x = 2000, y = 0.92, xend = 4000, yend = 0.92),
               arrow = arrow(type = "closed", angle = 20, length = unit(0.05, "inches")), color="black")+
  scale_color_viridis_d(name="Age Bin\n(mos)")+
  scale_fill_viridis_d(name="Age Bin\n(mos)")+
  #facet_wrap(~age_bin)+
  scale_y_continuous(breaks=seq(0.4,1,0.1),limits=c(0.4,1))+
  scale_x_continuous(breaks=seq(-1000,4000,1000),limits=c(-1050,4000))+
  xlab("Time from trial onset (ms)")+
  ylab("Proportion Target Looking")+
  theme_cowplot()+
  theme(legend.key.size = unit(0.3, 'cm'), #change legend key size
        legend.key.height = unit(0.3, 'cm'), #change legend key height
        legend.key.width = unit(0.3, 'cm'), #change legend key width
        legend.text = element_text(size=9),
        legend.title = element_text(size=9),
        legend.position=c(0.03,0.6),
        axis.title = element_text(size=12),
        axis.text = element_text(size=10))
```

>>>>

#overall plot
d_timecourse_by_age_overall |> 
  filter(age_bin!="<12") |> 
  filter(t_norm>-1000) |> 
  ggplot(aes(x=t_norm, y=accuracy, group=age_bin, color=age_bin)) +
  geom_rect(xmin=2000,xmax=4000,ymin=0,ymax=1.2,fill="#DFDFDF",color=NA,alpha=0.05)+
  geom_rect(xmin=200,xmax=2000,ymin=0,ymax=1.2,fill="#F2F2F2",color=NA,alpha=0.05)+
  geom_smooth(stat="identity", aes(y=accuracy, ymin=accuracy-sem, ymax=accuracy+sem,fill=age_bin))+
  #geom_smooth(stat="smooth")+
  geom_hline(yintercept=0.5, linetype="dashed")+
  geom_vline(xintercept=0, linetype="solid")+
  #add text
  annotate("text", x=50, y=0.85, label="Label Onset", hjust=0, vjust=0,size=3)+
  annotate("text", x=400, y=0.99, label="SHORT WINDOW",hjust=0, vjust=0,size=2.5)+
  annotate("text", x=1500, y=0.93, label="LONG WINDOW",hjust=0, vjust=0,size=2.5)+
  geom_segment(aes(x = 1000, y = 0.98, xend = 200, yend = 0.98),
               arrow = arrow(type = "closed", angle = 20, length = unit(0.05, "inches")), color="black")+
  geom_segment(aes(x = 1000, y = 0.98, xend = 2000, yend = 0.98),
               arrow = arrow(type = "closed", angle = 20, length = unit(0.05, "inches")), color="black")+
  geom_segment(aes(x = 2000, y = 0.92, xend = 200, yend = 0.92),
               arrow = arrow(type = "closed", angle = 20, length = unit(0.05, "inches")), color="black")+
  geom_segment(aes(x = 2000, y = 0.92, xend = 4000, yend = 0.92),
               arrow = arrow(type = "closed", angle = 20, length = unit(0.05, "inches")), color="black")+
  scale_color_viridis_d(name="Age Bin\n(mos)")+
  scale_fill_viridis_d(name="Age Bin\n(mos)")+
  #facet_wrap(~age_bin)+
  scale_y_continuous(breaks=seq(0.4,1,0.1),limits=c(0.4,1))+
  scale_x_continuous(breaks=seq(-1000,4000,1000),limits=c(-1050,4000))+
  xlab("Time from trial onset (ms)")+
  ylab("Proportion Target Looking")+
  theme_cowplot()+
  theme(legend.key.size = unit(0.3, 'cm'), #change legend key size
        legend.key.height = unit(0.3, 'cm'), #change legend key height
        legend.key.width = unit(0.3, 'cm'), #change legend key width
        legend.text = element_text(size=9),
        legend.title = element_text(size=9),
        legend.position=c(0.03,0.6),
        axis.title = element_text(size=12),
        axis.text = element_text(size=10))
```
